Index measures for oak decline severity using phenotypic descriptors

### 2020-03-04 manuscript/manuscript.Rmd
added discussion point on AOD classifed COD trees

```{r loadData, include = FALSE}
loadd(site_rf_margin,
      site_rf_post_correction_margin,
      PDI_status_ttest,
      DAI_groups_ttest,
      PDI_rf_tune_params,
      DAI_rf_tune_params,
      analysis_suitable_data,
      site_corrected_analysis_suitable_data,
      remission_PDI_group_ttest,
      remission_DAI_group_ttest,
      DAI_descriptor_importance,
      surveyors_names,
      pheno_data_with_additional_descriptors)
```

@@

>>>>

```{r loadData, include = FALSE}
loadd(site_rf_margin,
      site_rf_post_correction_margin,
      PDI_status_ttest,
      DAI_groups_ttest,
      PDI_rf_tune_params,
      DAI_rf_tune_params,
      analysis_suitable_data,
      site_corrected_analysis_suitable_data,
      remission_PDI_group_ttest,
      remission_DAI_group_ttest,
      DAI_descriptor_importance,
      surveyors_names,
      pheno_data_with_additional_descriptors,
      decline_indexes)
```

@@

There were `r decline_indexes %>% filter(ChosenGroup == 'COD',PDI > 0.5,DAI > 0.5) %>% nrow()` manually assigned COD trees that were scored with PDI and DAI values greater than 0.5, suggesting that they were in fact AOD trees.
These trees were manually assigned COD status due to the presence of *Armillaria* attack and associated bleeds.
While the phenotyping protocol used here made no distinction as to the biotic origin of the stem bleeds, it is interesting to note that not only do these trees have the presence of stem bleeds similar to AOD trees, but also share their relatively larger stature compared to the majority of COD trees.
This likely reflects a more acute and aggressive nature of the *Armillaria* infection in these trees with deterioration in crown health having occurred over a shorter time period. 
It therefore has less time in which to impact overall growth compared to the other COD trees. 
In this sense the DAI scale can be seen to differentiate decline types based less on the actual biotic agents involved in the interaction but more on the time-scales over which the trees themselves have been afflicted.
